---
title: "codebook Jaime Ortiz"
author: "Jaime Ortiz"
date: "July 7, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Codebook
========
Codebook was generated on `r as.character(Sys.time())` during the same process that generated the dataset. See `run_analysis.md` or `run_analysis.html` for details on dataset creation.

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(full.tidy)
```

List the key variables in the data table
----------------------------------------

```{r}
key(full.tidy)
```

Show a few rows of the dataset
------------------------------

```{r}
full.tidy
```

Summary of variables
--------------------

```{r}
summary(full.tidy)
```

List all possible combinations of features
------------------------------------------

```{r}
full.tidy[, .N, by=c(names(full.tidy)[grep("^feat", names(full.tidy))])]
```

Save to file
------------

Save data table objects to a tab-delimited text file called `DatasetActivity.txt`.

```{r save}
a <- file.path(path, "DatasetActivity.txt")
write.table(full.tidy, a, quote=FALSE, sep="\t", row.names=FALSE)
```